Titeln på avhandlingens språk

### 2022-08-28 model.tex
sample data

For the sub-model for the generation of realistic execution times, we employ a cleaned and re-parameterized copy of the timing data collected for~\cite{olguinmunoz:impact2021}.
This data consists of a table containing \num{6760} rows, where each row contains data for a single step and consists of four columns:
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and }}]
    \item a unique identifier for the participant from which the data was recorded
    \item the recorded \acl{TTF} for the current step
    \item the recorded execution time for the current step
    \item a normalized value for the neuroticism of the participant the data is from
\end{enumerate*}.

>>>>

For the sub-model for the generation of realistic execution times, we employ a cleaned and re-parameterized copy of the timing data collected for~\cite{olguinmunoz:impact2021}.
The data consists of timing information for each of the \num{169} steps performed by the \num{40} participants in the human-subject trials.
The resulting \num{6760} data points are arranged in a table, a sample of which can be seen in \cref{tab:data:exectime}, together with identifiers for the subjects and a normalized value of their neuroticism.

\begin{table}
\centering
\caption[A]{%
    Sample of the execution time data  used for the elaboration of the timing model.
    Rows contain the execution times and \acp{TTF} for each of the \num{169} steps performed by the \num{40} participants in \textcite{olguinmunoz:impact2021}, expressed in seconds, together with a unique identifier for the subject, their associated level of normalized neuroticism, and a sequence number identifying the position of the step in the task.
}\label{tab:data:exectime}
\begin{tabular}{rrrrrr}
    \toprule
    {seq} & {run\_id} & {exec\_time} & {ttf} & {neuroticism}\\
    \midrule
    1 & 134146 & 3.655 & 0.597 & 0.375\\
    2 & 134146 & 4.439 & 0.554 & 0.375\\
    3 & 134146 & 2.943 & 0.562 & 0.375\\
    \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) \\
    169 & 134146 & 3.532 & 4.571 & 0.375\\
    1 & 134470 & 3.461 & 0.561 & 0.594\\
    2 & 134470 & 6.678 & 0.572 & 0.594\\
    \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) \\
    \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) \\
    169 & 137353 & 4.615 & 0.537 & 0.625\\
    \bottomrule
    \end{tabular}
\end{table}
